### 2019-03-10 paper/sex_selection_spacing-ver2.tex
Prettier set-up for regional graphs

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r1}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r1}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r1}} 
\caption{high education - r1}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r2}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r2}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r2}} 
\caption{high education - r2}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r3}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r3}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r3}} 
\caption{high education - r3}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{Urban}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r4}} 
\\
\caption*{Rural}
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r4}} 
\subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r4}} 
\caption{high education - r4}
\end{figure}

>>>>

% \begin{figure}[htpb]
% \centering
% \caption*{Urban}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r1}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r1}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r1}} 
% \\
% \caption*{Rural}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r1}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r1}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r1}} 
% \caption{high education - r1}
% \end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r1}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r1} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_urban_r1}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r1}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r1} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_rural_r1} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight or more years of education - r1}
\label{fig:bootstrap_high_r1}
\end{figure}

% \begin{figure}[htpb]
% \centering
% \caption*{Urban}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r2}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r2}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r2}} 
% \\
% \caption*{Rural}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r2}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r2}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r2}} 
% \caption{high education - r2}
% \end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r2}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r2} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_urban_r2}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r2}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r2} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_rural_r2} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight or more years of education - r2}
\label{fig:bootstrap_high_r2}
\end{figure}

% \begin{figure}[htpb]
% \centering
% \caption*{Urban}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r3}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r3}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r3}} 
% \\
% \caption*{Rural}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r3}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r3}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r3}} 
% \caption{high education - r3}
% \end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r3}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r3} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r3}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r3} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight or more years of education - r3}
\label{fig:bootstrap_high_r3}
\end{figure}

% \begin{figure}[htpb]
% \centering
% \caption*{Urban}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_urban_r4}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_urban_r4}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_urban_r4}} 
% \\
% \caption*{Rural}
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell2_high_rural_r4}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell3_high_rural_r4}} 
% \subfloat[all]{\includegraphics[width=0.27\textwidth]{bs_spell4_high_rural_r4}} 
% \caption{high education - r4}
% \end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_r4}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_r4} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_r4}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_r4} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight or more years of education - r4}
\label{fig:bootstrap_high_r4}
\end{figure}
